Are Delayed Issues Harder to Resolve?

### 2016-01-01 phaseDelay4Emse.tex
Updates from ShareLaTeX

This paper documents the above studies and explores reasons for this  mismatch between this widely-held
belief and empirical data.
In  summary, DIE is not some constant across all projects. Rather, is may be an historical relic that only occurrs intermittently 
in  certain kinds of projects.  This is a significant result since it predicts that  new development
processes that promise to faster retire more issues will have only a  limited return on investment. 
\end{abstract}

@@

The respondents answered questions on two scales: \newline
\textbf{Agreement:} ``Based on your experience, do you agree that the statement above is correct?'' A Likert scale captured the agreement score from Strongly Disagree to Strongly Agree. A text box was provided to explain the answer. \newline
\textbf{Applicability:} ``To the extent that you believe it, how widely do you think it applies among software development contexts?'' The possible answers were: 
-1 meaning ``I don't know''; and 0 meaning ``this law does not apply at all'';
 1 meaning ``applies in a very narrow range of projects'';  2 meaning
``rarely applies'';   3 meaning
``occasionally applies'';  
4 meaning ``very frequently applies''; and
 5 meaning ``always applies''.
Respondents were required to explain the applicability score in a text box.

@@

\begin{figure}[!t] 
% \renewcommand{\baselinestretch}{0.8}
 \scriptsize
\begin{center}
\begin{tabular}{r|rrr|ll|rl}   
  \multicolumn{1}{c}{~} &\multicolumn{3}{c}{Percentiles}&\multicolumn{2}{c}{Phase}\\\cline{2-6}
N & 25th & 50th & 75th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline
 48&   14&   30&   51&Before&DesignInspect &1.00 & **********  \\
 53&   13&   28&   49&Before&CodeReview &0.93 & **********  \\
 94&   22&   45&   80&Before&CodeInspect &1.50 & ***************  \\
153&   38&   77&  130&Before&UnitTest &2.56 & **************************  \\
127&   30&   65&  128&Before&IntTest &2.16 & **********************  \\
 92&   24&   56&   89&Before&SysTest &1.86 & *******************  \\\hline

@@

235&   57&  115&  177&Code&CodeReview &1.00 &  **********  \\
228&   56&  113&  176&Code&CodeInspect &0.99 & ********** \\
243&   59&  125&  206&Code&IntTest &1.08 &     *********** \\
191&   46&   95&  173&Code&SysTest &0.82 &     ******** \\
269&   66&  133&  206&Code&UnitTest &1.15 &    ***********  \\
130&   31&   65&  122&Code&AcceptTest &0.56 &  ******  \\
 \end{tabular}
\end{center}
\caption{Distribution of fix times seen in SEI TSP data. Left hand side bars
show scale up on median values.
}
\label{fig:raw}
\end{figure}

\begin{figure}[!t] 
 %\renewcommand{\baselinestretch}{0.8}
 \scriptsize
\begin{center}
\begin{tabular}{r|r|ll|rl}   
  \multicolumn{1}{c}{~} &\multicolumn{1}{c}{Percentiles}&\multicolumn{2}{c}{Phase}\\\cline{2-4}
N  & 99th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline

57&257&Before&Code&1.00&*********\\
72&153&Before&CodeInspect&0.60&****** \\
165&282&Before&Test&1.01&**********\\
50&365&Before&IntTest&1.42&************** \\
42&151&Before&SysTest&0.59&****** \\\hline 
37&600&Design&Design&1.00&********** \\
455&277&Design&DesignInspect&0.46&***** \\
218&240&Design&Code&0.40&**** \\
166&163&Design&CodeInspect&0.27&*** \\
542&652&Design&Test&1.09&***********\\
67&277&Design&IntTest&0.46&***** \\
92&480&Design&SysTest&0.80&******** \\\hline 
126&600&Code&Code&1.0&**********\\
459&243&Code&CodeInspect&0.4&**** \\
461&365&Code&Test&0.6&****** \\
230&290&Code&SysTest&0.5&***** \\
71&600&Code&AcceptTest&1.0&*********\\
348&7200&Code&IntTest&12.0&************************************\\
  &    &    &       &    & ************************************\\
  &    &    &       &    & ************************************\\

\end{tabular}
\end{center}
\caption{99th percentile scale ups.}
\label{fig:scale99}
\end{figure}

\newpage
\subsection{Observations from 171 Projects}

>>>>

This paper documents the above studies and explores reasons for this  mismatch between this widely-held
belief and empirical data.
In  summary, DIE is not some constant across all projects. Rather, DIE might
actually be an historical relic that  occurs intermittently 
only in  certain kinds of infrequently occuring projects.  This is a significant result since it predicts that  new development
processes that promise to faster retire more issues will have only a  limited return on investment. 
\end{abstract}

@@

The respondents answered questions on two scales:

\bi
\item
\textbf{Agreement:} ``Based on your experience, do you agree that the statement above is correct?'' A Likert scale captured the agreement score from Strongly Disagree to Strongly Agree. A text box was provided to explain the answer. \newline
\item
\textbf{Applicability:} ``To the extent that you believe it, how widely do you think it applies among software development contexts?'' The possible answers were: 
-1 meaning ``I don't know''; and 0 meaning ``this law does not apply at all'';
 1 meaning ``applies in a very narrow range of projects'';  2 meaning
``rarely applies'';   3 meaning
``occasionally applies'';  
4 meaning ``very frequently applies''; and
 5 meaning ``always applies''.
Respondents were required to explain the applicability score in a text box.
\ei

@@

\begin{figure} 
% \renewcommand{\baselinestretch}{0.8}
 \scriptsize
\begin{center}
\begin{tabular}{r|rrr|ll|rl}   
  \multicolumn{1}{c}{~} &\multicolumn{3}{c}{Percentiles}&\multicolumn{2}{c}{Phase}\\\cline{2-6}
N & 25th & 50th & 75th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline
 48&   14&   30&   51&Before&DesignInspect &1.00 & **********  \\
 53&   13&   28&   49&Before&CodeReview &0.93 & **********  \\
 94&   22&   45&   80&Before&CodeInspect &1.50 & ***************  \\
153&   38&   77&  130&Before&UnitTest &2.56 & **************************  \\
127&   30&   65&  128&Before&IntTest &2.16 & **********************  \\
 92&   24&   56&   89&Before&SysTest &1.86 & *******************  \\\hline

@@

235&   57&  115&  177&Code&CodeReview &1.00 &  **********  \\
228&   56&  113&  176&Code&CodeInspect &0.99 & ********** \\
243&   59&  125&  206&Code&IntTest &1.08 &     *********** \\
191&   46&   95&  173&Code&SysTest &0.82 &     ******** \\
269&   66&  133&  206&Code&UnitTest &1.15 &    ***********  \\
130&   31&   65&  122&Code&AcceptTest &0.56 &  ******  \\
 \end{tabular}
\end{center}
\caption{ SEI TSP data: distribution of fix times. RHS bars
show scale up on {\bf  50th percent} values (i.e. the median).
}
\label{fig:raw}
\end{figure}

\begin{figure} 
 %\renewcommand{\baselinestretch}{0.8}
 \scriptsize
\begin{center}
\begin{tabular}{r|r|ll|rl}   
  \multicolumn{1}{c}{~} &\multicolumn{1}{c}{Percentiles}&\multicolumn{2}{c}{Phase}\\\cline{2-4}
N  & 99th &   injected & removed   & \multicolumn{2}{l}{Scale up w.r.t. to first phase}\\\hline

57&257&Before&Code&1.00&*********\\
72&153&Before&CodeInspect&0.60&****** \\
165&282&Before&Test&1.01&**********\\
50&365&Before&IntTest&1.42&************** \\
42&151&Before&SysTest&0.59&****** \\\hline 
37&600&Design&Design&1.00&********** \\
455&277&Design&DesignInspect&0.46&***** \\
218&240&Design&Code&0.40&**** \\
166&163&Design&CodeInspect&0.27&*** \\
542&652&Design&Test&1.09&***********\\
67&277&Design&IntTest&0.46&***** \\
92&480&Design&SysTest&0.80&******** \\\hline 
126&600&Code&Code&1.0&**********\\
459&243&Code&CodeInspect&0.4&**** \\
461&365&Code&Test&0.6&****** \\
348&720&Code&IntTest&1.2&************\\
230&290&Code&SysTest&0.5&***** \\
71&600&Code&AcceptTest&1.0&*********

\end{tabular}
\end{center}
\caption{SEI TSP data: distribution of fix times. RHS bars
show scale up on {\bf 99th percent} values.}
\label{fig:scale99}
\end{figure}

\subsection{Observations from 171 Projects}
